---
title: "How Yelp can Support a New Business"
author: "David Chiang, Johnny Yang, Justin Bao, Siddharth Jayadev"
date: "5/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr")
library("leaflet")
source("scripts/barchart.R")
source("scripts/map.R")
source("scripts/scatterplot.R")
yelp_df <- read.csv("data/yelp.csv", stringsAsFactors = FALSE)
```


## Purpose of the Project
Yelp is becoming a growing platform for digital marketing. In our current day
and age, having a effective digital presence on the internet can be vital to the
success of a business. Through the Yelp Dataset, we hope to be able to discover
insights that will help a new business be successful in their environment. For 
this project, we will be specifically focusing on the city of Las Vegas and the 
Yelp data involved. The source of our data is
[Yelp Data Set](https://www.yelp.com/dataset/challenge).

## Map of Las Vegas Businesses
```{r map, echo = FALSE, warnings = FALSE}
map_chart(yelp_df)
```


## Bar Chart of Price Ranges in Las Vegas
```{r bar_chart, echo = FALSE, warnings = FALSE}
bar_chart(yelp_df)
```

## Scatter Plot of Check-Ins Versus Reviews
```{r bar_chart, echo = FALSE, warnings = FALSE}
scatter_plot(yelp_df)
```


