---
title: "How Yelp can Support a New Business"
author: "David Chiang, Johnny Yang, Justin Bao, Siddharth Jayadev"
date: "5/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr")
library("leaflet")
source("scripts/barchart.R")
source("scripts/map.R")
source("scripts/top_1000_map.R")
source("scripts/scatterplot.R")
source("scripts/summary.R")
yelp_df <- read.csv("data/yelp.csv", stringsAsFactors = FALSE)
```

## Purpose of the Project
Yelp is becoming a growing platform for digital marketing. In our current day
and age, having a effective digital presence on the internet can be vital to the
success of a business. Through the Yelp Dataset, we hope to be able to discover
insights that will help a new business be successful in their environment. For 
this project, we will be specifically focusing on the city of Las Vegas and the 
Yelp data involved. The source of our data is
[Yelp Data Set](https://www.yelp.com/dataset/challenge).

## Summary Statistics 
The total number of restaurants reviewed on Yelp for Las Vegas is `r restaurants_reviewed`. `r total_tip_count` people tipped in Las Vegas and North Las Vegas. The average star rating of the restaurants in Las Vegas and North Las Vegas is `r avg_star_rating`. The most reviewed restaurant was `r most_reviewed`. The summary data for price range(Min, 1st Quartile, Median, Mean, 3rd Quartile, Max, NA's) is `r summary_range`.

## Summary Table by Rating

The following summary table groups the data by star ratings and calculates the total number of checkins, tips and reviews. The star rating is arranged in ascending order. By arranging the data in this way we can know the summary about the various star-ratings.

```{r, echo=FALSE}
kable(star_wise, col.names = c("Rating", "Checkins" ,"Tips" , "Reviews"))
```

The most number of checkins, tips, and reviews were at restaurants with rating 4.0. This means people reviews on Yelp mostly if they find the place is worth a 4.0 rating.

## Map of Las Vegas Businesses
```{r map, echo = FALSE, warnings = FALSE}
map_chart(yelp_df)
```
This map of Las Vegas shows the star rating of every single business on Yelp.
The color designates the star rating for the business. It is intended to allow 
a user to zoom into a specific are and see if it is concentrated with a specific star rating. In the future, we will be attempting to create a shiny UI that 
allows users to see where there are 1-star, 2-star, 3-star, 4-star, and 5-star businesses. In a broad scope, the map shows that a majority of businesses in 
Las Vegas regardless of region is rated 4-star and 5-star

## Map of Businesses with over 1000 Reviews
```{r top_1000_map, echo= FALSE, warnings = FALSE}
Business_with_1000_map(yelp_df)
```
This map of Las Vegas is filtered by businesses with over 1000 reviews in
Las Vegas. The total number of businesses with over 1000 reviews is 
104 businesses. When a user clicks on a point, they will get information such as 
the name, number of check-ins, and the average star rating of the restaurant. 
We hope that this will give the user an idea of what the top businesses in 
Las Vegas according to Yelp would be.  We chose the map so that users can see the vicinity or area with the top businesses. 

## Bar Chart of Price Ranges in Las Vegas
```{r bar_chart, echo = FALSE, warnings = FALSE}
bar_chart(yelp_df)
```

Above is a bar chart of the different price levels for businesses in the Las
Vegas region. We included this to show prospective business owners on what 
the most common price level is for businesses in the area. This bar graph 
demonstrates that a majority of restaurants were in the $11-$30 range.

## Scatter Plot of Check-Ins Versus Reviews
```{r scatterplot.R, echo = FALSE, warnings = FALSE}
scatter_plot(yelp_df)
```

We wanted to find the correlation of people that were checking into the business
and see if they were also leaving a review. We found that a majority of the
people that checked in did not end up leaving a review. We wanted to include 
this to allow prospective businesses to see if running check-in promotions 
would increase the amount of positive reviews on their Yelp profile.
